SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-25 scipy-1.0/ckdtree.tex
Updated dual tree algorithm reference to match source code; fixed typo in ckdtree tech improvements section.

The cKDTree module implements a dual tree counting algorithm\cite{pmlr-v28-curtin13},
with an improvement to the pair counting algorithm to improve the scaling
with the number of bins. The cKDTree can now be augmented by weights, with 
weighted paircount essential in many scientific applications, e.g. computing 
correlation function of galaxies\cite{0004-637X-750-1-38}.

>>>>

The cKDTree module implements a dual tree counting algorithm\cite{Moore2000ar},
with an improvement to the pair counting algorithm to improve the scaling
with the number of bins. The cKDTree can now be augmented by weights, with 
weighted paircount essential in many scientific applications, e.g. computing 
correlation functions of galaxies\cite{0004-637X-750-1-38}.
